\documentclass{article}

\usepackage{hyperref}

\title{The OpenSMT Solver in SMT-COMP 2019}
\author{
Martin Blicha \and 
Antti E. J. Hyv{\"a}rinen \and
Matteo Marescotti \and
Natasha Sharygina \\
{\small Universit{\`a} della Svizzera italiana (USI), Lugano,
Switzerland}
}
\date{}
\begin{document}
\maketitle

\section{Overview}

OpenSMT~\cite{HyvarinenMAS16} is a T-DPLL based SMT
solver~\cite{NieuwenhuisOT:JACM06} that has been developed at USI,
Switzerland, since 2008.  The solver is written in {\tt C++} and
currently supports the quantifier-free logics of equality with
uninterpreted functions (QF\_UF), and linear real arithmetic (QF\_LRA).
The solver has a rudimentary support for quantifier-free linear integer
arithmetic (QF\_LIA) based on branch-and-bound, and supports some
aspects of bit-vector logic.

In comparison to 2018, the 2019 competition entry features a wide range
of performance improvements in simplification, the Simplex algorithm,
and the Egraph algorithm, several bug fixes related to solver soundness,
and improved support for the logics.  In the process, the solver
high-level architecture improved and low-level code cleaning resulted in
fewer compiler warnings.

The solver development process is better defined in comparison to the
previous state.  The main public repository
 is now
hosted in GitHub, where the commit process is integrated with Travis CI
to ensure the passing of regression tests and different compilation.
Commits are integrated to the master branch through pull requests once
they pass a human review and the Travis CI configuration.

OpenSMT features not exercised in the competition include support for a
wide range of interpolation algorithms for propositional
logic~\cite{AltFHS:VSTTE2015}, linear real
arithmetic~\cite{BlichaHKS19}, and uninterpreted
functions~\cite{AltHAS:FMCAD17}; an experimental look\-ahead-based
search algorithm~\cite{HyvarinenMSCS18} as an alternative to the more
standard CDCL algorithm; and features that support search-space
partitioning in particular designed for parallel
solving~\cite{HyvarinenMS:SAT15}.

\section{External Code and Contributors}

The SAT solver driving OpenSMT is based on the MiniSAT
solver~\cite{EenS:SAT03}, and the rational number implementation is
inspired by a library written by David Monniaux.  Several people have
directly contributed to the OpenSMT code.  In alphabetical order, the
major contributors are
%
Leonardo Alt,
Sepideh Asadi,
Martin Blicha,
Roberto Bruttomesso,
Antti E. J. Hyv{\"a}rinen,
Matteo Marescotti,
Edgar Pek,
Simone Fulvio Rollini,
Parvin Sadigova, and
Aliaksei Tsitovich.
%
The solver is being developed in Natasha Sharygina's software
verification group at USI.

\section{Utilization}

OpenSMT is being used in a range of projects as a back-end solver.  It
does interpolation for the Sally model checker~\cite{JovanovicD:FMCAD16}
which won the transition systems category in the constrained horn clause
competition 2019.  OpenSMT also forms the basis of our own model
checkers such as HiFrog~\cite{AltACMFHS17}.  OpenSMT is compatible with
the parallelization engine SMTS~\cite{MarescottiHS18}.

\section{Download}
The solver source code is available at

\url{https://github.com/usi-verification-and-security/opensmt}.

\iffalse
in chronological order, work on interpolation 
algorithms~\cite{BlichaHKS19,AltHAS17,JancikAFHKS16,AsadiBFHESC18}
and parallel SMT 
solving~\cite{HyvarinenMSCS18,MarescottiHS18,HyvarinenMS:SAT15}.
OpenSMT2 is
used as the back-end in model-checking tools
HiFrog~\cite{AltACMFHS17},
eVolCheck~\cite{FSS_TACAS13}, 
FunFrog~\cite{SFS_ATVA12}, and
PeRIPLO~\cite{RolliniAFHS:LPAR2013,AltFHS:VSTTE2015}.
OpenSMT2 is a supported engine in the parallel 
solving framework SMTS~\cite{MarescottiHS16}.

\section{Acknowledgements}
We thank everyone who helped
developing OpenSMT2. In particular,
Leonardo Alt,
Sepideh Asadi,
Martin Blicha,
Roberto Bruttomesso,
Antti E. J. Hyv{\"a}rinen,
Matteo Marescotti,
Edgar Pek,
Simone Fulvio Rollini, 
Parvin Sadigova,
Natasha Sharygina,
Aliaksei Tsitovich.
\fi

\bibliography{abstract}
\bibliographystyle{plain}

\end{document}
